Demanding resources: Agreement across characteristics seen as both challenges and resources

### 2022-10-12 SIOP2023/Counts/convergence.Rmd
JDR #3

An abundance of research applying the job demands-resources model [@demerouti2001job] and job demands-resources theory [@bakker2017job] underscores the importance of job characteristics on the experience of work. Resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. Demands, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain [e.g., high work pressure, @demerouti2001job]. These two categories of outcomes (e.g., "good" and "bad") are thought to occur via one of two different mechanisms: motivational (resulting from resources) or health impairment [resulting from demands, @bakker2014job]. Much of our existing research on the JD-R assumes that certain characteristics (for example, autonomy) are resources and others (for example, time constraints) are generally considered demands. This study searches instead for circumstances that provide exception to this static dichotomy of job characteristic mutual exclusivity.

@@

Prior to proposing specific predictions regarding the current SIOP presentation, the empirical evidence on challenge and hindrance demands is very briefly shared below. To begin, the first logical question is whether employees actually distinguish between challenges and hindrances, and research suggests that they can and do. For example, @bakker2013weekly found that perceived work pressure can be classified as a hindrance demand, and emotional demands as a challenge demand. @webster2011extending considered three common workplace demands including workload, role ambiguity, and role conflict. Interestingly, they found that while each could be appraised primarily as challenges or hindrances, employees could also simultaneously be perceived as being both a challenge and hindrance.

@@

We explored the agreement of perceptions of job characteristics as resources as well as demands (in the form of challenges and hindrances). Given the definitions of each (i.e.,  aspect of one’s job that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development [resource] vs. aspect of one’s job that can promote mastery, personal growth, or future gains [challenge]), we propose respondents may consider the same characteristic to be viewed as both a challenge as well as a resource. That is, we explore whether these perceptions are orthogonal, contradictory, or perhaps even complimentary. Utilizing the job demands-resources theory and the challenge-hindrance framework, we propose that job characteristics appraised as “challenge demands” (i.e., promote mastery, personal growth, and future gains) may also be viewed as job resources.

@@

Although the same job characteristic may be percieved as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others. For example, a physically strenuous job requirement such as "carrying heavy objects" would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as "negotiating work schedules" may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge. O\*Net has different levels of abstraction with regard to the nature of job characteristic, we will be exploring a mid-level abstraction with seven different characteristic "scales".

@@

We evaluate agreement across perceptions of present job characteristics regarding their characterization of resource, challenge, and hindrance (Bakker & Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001). To capture an effectively exhaustive list of characteristics that apply to, theoretically, *every* possible job, we consult the  unifying framework of O\*Net.

@@

Our survey consisted of 98 items crafted from job characteristic descriptors located within O\*Net’s classification of “work activities”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context” groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).

@@

>put example response scale in

Subsequent to providing ratings of whether or not each of the 98 O\*Net characteristics were relevant for the respondent’s work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) . . . this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) . . . this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) . . . this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.

The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).

@@

>Note. Should probably run a quick anova on these

@@

Figure \@ref(fig:recchall) explores the possibility of moderation by *type of characteristic rated* for the resource-challenge convergence. Here we categorized each characteristic by its O\*Net "scale" (one of seven), and the graph shows greater consistency across certain characteristics (for example, *Mental Processes* or *Interacting with Others*) and less convergence across other *types* of job activities (for example, *Physical* characteristics). A repeated-measures ANOVA retaining these 7 scales as independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001 (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.

@@

Our findings highlight the importance of dissociating the *nature* of job demands. Similar to the eustress/distress distinction [e.g., @selye1974stress], it would seem as though demands should be thought of in a valenced manner (e.g., is it a "good" demand or a "bad" demand)[^bootsie].

[^bootsie]: Beyond this SIOP presentation, we have further investigated differential associations of challenges and hindrances with "good" and "bad" outcomes, but have not confirmed meaningful differential associations within this current dataset.

The major goal of this paper was to further explore the relationships among total perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout. Additionally, we considered whether resources and challenge demands were perceived as distinct, and finally, whether the patterns were similar across job categories/types of work. The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a). Employers would benefit from understanding that at leas the perception of having “more” resources and more challenge demands in a job is highly associated with reported engagement. While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless. The other relationships with outcomes of stress and burnout were not supported, suggesting that the sheer number of resources, challenges, and hindrances are not significantly related to these negative outcomes. It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
 Further, total resources were highly associated challenge demands (supporting H4). We could even argue, given the magnitude of the correlation, that they are capturing the same thing (74% overlap with a correlation of .86). Need to also talk about our exploratory findings regarding patterns across job type

We conceptualized resources and demands in terms of perceived total amounts.

The dissociation of challenges and hindrances may be important moving forward. @cavanaugh2000empirical found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers. However, @abbas2019challenge found that challenge and hindrance stressors were both positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (@crawford2010linking). The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator. @gerich2017relevance, for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands. To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, @podsakoff2007differential meta-analysis supported the original assertion of @cavanaugh2000empirical such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.

>>>>

An abundance of research applying the job demands-resources model [@demerouti2001job] and job demands-resources theory [@bakker2017job] underscores the importance of job characteristics on the experience of work. Resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. Demands, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain [e.g., high work pressure, @demerouti2001job]. These two categories of outcomes (e.g., "good" and "bad") are thought to occur via one of two different mechanisms: motivational (resulting from resources) or health impairment [resulting from demands, @bakker2014job]. Much of our existing research on the JD-R assumes that certain characteristics (for example, autonomy) are resources and others (for example, time constraints) are generally considered demands. This study searches instead for circumstances that provide exception to this mutually exclusive dichotomy of job characteristics.

@@

Prior to proposing specific predictions regarding the current SIOP presentation, the empirical evidence on challenge and hindrance demands is very briefly shared below. To begin, the first logical question is whether employees actually distinguish between challenges and hindrances, and research suggests that they can and do. For example, @bakker2013weekly found that perceived work pressure can be classified as a hindrance demand, while the requirement to express emotions is a challenge demand. @webster2011extending also considered three common work characteristics including workload, role ambiguity, and role conflict. Interestingly, they found that while each could be identified *primarily* as a challenge or hindrance, employees could also appraise that a characteristic is simulataneously both a challenge and hindrance.

Although it is cleaner to be able to categorize job characteristics as *either* a demand or a resource, the above research suggests that an individual's (perhaps unique) appraisal is at least occasionally an important consideration. It is quite possible that one person experiences high work pressure (commonly cited as a demand in the literature) as a hindrance stressor and thus experiences strain, and another thrives in a fast-paced pressured role and would thus find the environment motivating.

@@

We explored the extent to which perceptions of job characteristics converge upon being uniquely or concurrently experienced as resources and demands (in the form of challenges and hindrances). Our supposition is that respondents may consider the same objective job characteristic to be both challenging and resourceful - if not at the same moment, at least at different points in time or under differing circumstances.

### Value of consulting O\*Net.

The Occupational Information Network (O\*NET; onetonline.org) contains a fairly comprehensive description of occupations [@peterson2001understanding]. This widely accessed database houses hundreds of standardized and occupation-specific descriptors for the majority of occupations within the United States, and these descriptions are frequently updated. These data, and the tools provided for public consumption on the website (e.g., Career Exploration Tools, “My Next Move”, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist interested or curious job-seekers discover the nature of work as well as skills and training typically required for different occupations. It is also often useful to employers by providing them with information that may be helpful in a job analysis context.

We asked our respondents to select job characteristics that were relevent to them from the broader comprehensive O\*Net list. We then asked these individuals to also rate those (relevant) characteristics in terms of their status as hindrances, challenges, and resources. Utilizing the job demands-resources theory and the challenge-hindrance framework, we propose that job characteristics appraised as “challenge demands” (i.e., promote mastery, personal growth, and future gains) may also be viewed as job resources.

@@

Although the same job characteristic may be percieved as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others. For example, a physically strenuous job requirement such as "carrying heavy objects" would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as "negotiating work schedules" may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge. O\*Net has different levels of abstraction with regard to the nature of job characteristic. We will be exploring a mid-level abstraction with seven different characteristic "scales".

@@

We evaluate agreement across perceptions of job characteristics regarding their characterization as resource, challenge, and hindrance (Bakker & Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001). To capture an effectively exhaustive list of characteristics that apply to, theoretically, *every* possible job, we consult the  unifying framework of O\*Net.

@@

Our survey was informed by 98 statements taken from job characteristic descriptors located within O\*Net’s classification of “work activities”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context” groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).

@@

Subsequent to providing ratings of whether or not each of the 98 O\*Net characteristics were relevant for the respondent’s work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) . . . this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) . . . this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) . . . this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment. 
The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).

@@

@@

Figure \@ref(fig:recchall) explores the possibility of moderation by *type of characteristic rated* for the resource-challenge convergence. Here we categorized each characteristic by its O\*Net "scale" (one of seven), and the graph shows greater consistency across certain characteristics (for example, *Mental Processes* or *Interacting with Others*) and less convergence across other *types* of job activities (for example, *Physical* characteristics). A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001 (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.

@@

The major goal of this paper was to further explore the relationships among perceptions of job characteristics as challenge demands, hindrance demands, and resources. Our findings perhaps most noteably highlight the importance of dissociating the *nature* of job demands. Similar to the eustress/distress distinction [e.g., @selye1974stress], it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a "good" demand or a "bad" demand). We did not probe for dependent variable associations, however, @cavanaugh2000empirical found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite patterns in a sample of managers. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (@crawford2010linking). @podsakoff2007differential's meta-analysis also found that challenge demands were positively related to job satisfaction and organizational commitment and negatively related to both turnover intentions and actual turnover, while hindrance demands again produced the opposite patterns of relationship. Although we did not probe for outcome associations, the current study does suggest that hindrance demands also operate in a manner different than challenge demands with regard to their association with resource appraisals.

In terms of convergence of resource and challenge appraisals, there was quite a bit of variability (e.g., Figure \@ref(fig:percagree)), but that variability was partially explained by the nature of the characteristic being evaluated (e.g., Figure \@ref(fig:recchall)). Physical job characteristics such as, for example, the amount of "time spent bending or twisting the body" may be much more likely to be appraised as a challenging demand (but not a resource). Other *types* of job requirements, however, such as a mental process like, "scheduling work and activities" might reasonably be expected to exhibit greater convergence. We suspect that there are other moderators that help explain this association/ disassociation between challenges and resources, and would like to incorporate variables such as a respondents' personality in future investigations.

### 2022-10-12 SIOP2023/Counts/convergence.tex
JDR #3

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Demanding resources: Agreement across characteristics seen as both challenges and resources},
  pdfauthor={John Kulas1 \& Alicia Stachowski2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

An abundance of research applying the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017) underscores the importance of job characteristics on the experience of work. Resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). Demands, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure, Demerouti et al., 2001). These two categories of outcomes (e.g., ``good'' and ``bad'') are thought to occur via one of two different mechanisms: motivational (resulting from resources) or health impairment (resulting from demands, Bakker \& Demerouti, 2014). Much of our existing research on the JD-R assumes that certain characteristics (for example, autonomy) are resources and others (for example, time constraints) are generally considered demands. This study searches instead for circumstances that provide exception to this static dichotomy of job characteristic mutual exclusivity.

@@

Prior to proposing specific predictions regarding the current SIOP presentation, the empirical evidence on challenge and hindrance demands is very briefly shared below. To begin, the first logical question is whether employees actually distinguish between challenges and hindrances, and research suggests that they can and do. For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, and emotional demands as a challenge demand. Webster et al. (2011) considered three common workplace demands including workload, role ambiguity, and role conflict. Interestingly, they found that while each could be appraised primarily as challenges or hindrances, employees could also simultaneously be perceived as being both a challenge and hindrance.

@@

We explored the agreement of perceptions of job characteristics as resources as well as demands (in the form of challenges and hindrances). Given the definitions of each (i.e., aspect of one's job that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development {[}resource{]} vs.~aspect of one's job that can promote mastery, personal growth, or future gains {[}challenge{]}), we propose respondents may consider the same characteristic to be viewed as both a challenge as well as a resource. That is, we explore whether these perceptions are orthogonal, contradictory, or perhaps even complimentary. Utilizing the job demands-resources theory and the challenge-hindrance framework, we propose that job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) may also be viewed as job resources.

@@

Although the same job characteristic may be percieved as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others. For example, a physically strenuous job requirement such as ``carrying heavy objects'' would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as ``negotiating work schedules'' may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge. O*Net has different levels of abstraction with regard to the nature of job characteristic, we will be exploring a mid-level abstraction with seven different characteristic ``scales''.

@@

We evaluate agreement across perceptions of present job characteristics regarding their characterization of resource, challenge, and hindrance (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001). To capture an effectively exhaustive list of characteristics that apply to, theoretically, \emph{every} possible job, we consult the unifying framework of O*Net.

@@

Our survey consisted of 98 items crafted from job characteristic descriptors located within O*Net's classification of ``work activities'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'' groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).

@@

\begin{quote}
put example response scale in
\end{quote}

Subsequent to providing ratings of whether or not each of the 98 O*Net characteristics were relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) . . . this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) . . . this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) . . . this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.

The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).

@@

\begin{quote}
Note. Should probably run a quick anova on these
\end{quote}

@@

Figure \ref{fig:recchall} explores the possibility of moderation by \emph{type of characteristic rated} for the resource-challenge convergence. Here we categorized each characteristic by its O*Net ``scale'' (one of seven), and the graph shows greater consistency across certain characteristics (for example, \emph{Mental Processes} or \emph{Interacting with Others}) and less convergence across other \emph{types} of job activities (for example, \emph{Physical} characteristics). A repeated-measures ANOVA retaining these 7 scales as independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.

@@

Our findings highlight the importance of dissociating the \emph{nature} of job demands. Similar to the eustress/distress distinction (e.g., Selye, 1974), it would seem as though demands should be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand)\footnote{Beyond this SIOP presentation, we have further investigated differential associations of challenges and hindrances with ``good'' and ``bad'' outcomes, but have not confirmed meaningful differential associations within this current dataset.}.

The major goal of this paper was to further explore the relationships among total perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout. Additionally, we considered whether resources and challenge demands were perceived as distinct, and finally, whether the patterns were similar across job categories/types of work. The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a). Employers would benefit from understanding that at leas the perception of having ``more'' resources and more challenge demands in a job is highly associated with reported engagement. While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless. The other relationships with outcomes of stress and burnout were not supported, suggesting that the sheer number of resources, challenges, and hindrances are not significantly related to these negative outcomes. It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
Further, total resources were highly associated challenge demands (supporting H4). We could even argue, given the magnitude of the correlation, that they are capturing the same thing (74\% overlap with a correlation of .86). Need to also talk about our exploratory findings regarding patterns across job type

We conceptualized resources and demands in terms of perceived total amounts.

The dissociation of challenges and hindrances may be important moving forward. Cavanaugh et al. (2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers. However, Abbas and Raja (2019) found that challenge and hindrance stressors were both positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al. (2010)). The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator. Gerich (2017), for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands. To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, Podsakoff et al. (2007) meta-analysis supported the original assertion of Cavanaugh et al. (2000) such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.

\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.

@@

\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Demanding resources: Agreement across characteristics seen as both challenges and resources},
  pdfauthor={John Kulas1 \& Alicia Stachowski2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

An abundance of research applying the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017) underscores the importance of job characteristics on the experience of work. Resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). Demands, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure, Demerouti et al., 2001). These two categories of outcomes (e.g., ``good'' and ``bad'') are thought to occur via one of two different mechanisms: motivational (resulting from resources) or health impairment (resulting from demands, Bakker \& Demerouti, 2014). Much of our existing research on the JD-R assumes that certain characteristics (for example, autonomy) are resources and others (for example, time constraints) are generally considered demands. This study searches instead for circumstances that provide exception to this mutually exclusive dichotomy of job characteristics.

@@

Prior to proposing specific predictions regarding the current SIOP presentation, the empirical evidence on challenge and hindrance demands is very briefly shared below. To begin, the first logical question is whether employees actually distinguish between challenges and hindrances, and research suggests that they can and do. For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, while the requirement to express emotions is a challenge demand. Webster et al. (2011) also considered three common work characteristics including workload, role ambiguity, and role conflict. Interestingly, they found that while each could be identified \emph{primarily} as a challenge or hindrance, employees could also appraise that a characteristic is simulataneously both a challenge and hindrance.

Although it is cleaner to be able to categorize job characteristics as \emph{either} a demand or a resource, the above research suggests that an individual's (perhaps unique) appraisal is at least occasionally an important consideration. It is quite possible that one person experiences high work pressure (commonly cited as a demand in the literature) as a hindrance stressor and thus experiences strain, and another thrives in a fast-paced pressured role and would thus find the environment motivating.

@@

We explored the extent to which perceptions of job characteristics converge upon being uniquely or concurrently experienced as resources and demands (in the form of challenges and hindrances). Our supposition is that respondents may consider the same objective job characteristic to be both challenging and resourceful - if not at the same moment, at least at different points in time or under differing circumstances.

\hypertarget{value-of-consulting-onet.}{%
\subsubsection{Value of consulting O*Net.}\label{value-of-consulting-onet.}}

The Occupational Information Network (O*NET; onetonline.org) contains a fairly comprehensive description of occupations (Peterson et al., 2001). This widely accessed database houses hundreds of standardized and occupation-specific descriptors for the majority of occupations within the United States, and these descriptions are frequently updated. These data, and the tools provided for public consumption on the website (e.g., Career Exploration Tools, ``My Next Move'', Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist interested or curious job-seekers discover the nature of work as well as skills and training typically required for different occupations. It is also often useful to employers by providing them with information that may be helpful in a job analysis context.

We asked our respondents to select job characteristics that were relevent to them from the broader comprehensive O*Net list. We then asked these individuals to also rate those (relevant) characteristics in terms of their status as hindrances, challenges, and resources. Utilizing the job demands-resources theory and the challenge-hindrance framework, we propose that job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) may also be viewed as job resources.

@@

Although the same job characteristic may be percieved as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others. For example, a physically strenuous job requirement such as ``carrying heavy objects'' would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as ``negotiating work schedules'' may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge. O*Net has different levels of abstraction with regard to the nature of job characteristic. We will be exploring a mid-level abstraction with seven different characteristic ``scales''.

@@

We evaluate agreement across perceptions of job characteristics regarding their characterization as resource, challenge, and hindrance (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001). To capture an effectively exhaustive list of characteristics that apply to, theoretically, \emph{every} possible job, we consult the unifying framework of O*Net.

@@

Our survey was informed by 98 statements taken from job characteristic descriptors located within O*Net's classification of ``work activities'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'' groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).

@@

Subsequent to providing ratings of whether or not each of the 98 O*Net characteristics were relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) . . . this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) . . . this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) . . . this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).

@@

@@

Figure \ref{fig:recchall} explores the possibility of moderation by \emph{type of characteristic rated} for the resource-challenge convergence. Here we categorized each characteristic by its O*Net ``scale'' (one of seven), and the graph shows greater consistency across certain characteristics (for example, \emph{Mental Processes} or \emph{Interacting with Others}) and less convergence across other \emph{types} of job activities (for example, \emph{Physical} characteristics). A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.

@@

The major goal of this paper was to further explore the relationships among perceptions of job characteristics as challenge demands, hindrance demands, and resources. Our findings perhaps most noteably highlight the importance of dissociating the \emph{nature} of job demands. Similar to the eustress/distress distinction (e.g., Selye, 1974), it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand). We did not probe for dependent variable associations, however, Cavanaugh et al. (2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite patterns in a sample of managers. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al. (2010)). Podsakoff et al. (2007)'s meta-analysis also found that challenge demands were positively related to job satisfaction and organizational commitment and negatively related to both turnover intentions and actual turnover, while hindrance demands again produced the opposite patterns of relationship. Although we did not probe for outcome associations, the current study does suggest that hindrance demands also operate in a manner different than challenge demands with regard to their association with resource appraisals.

In terms of convergence of resource and challenge appraisals, there was quite a bit of variability (e.g., Figure \ref{fig:percagree}), but that variability was partially explained by the nature of the characteristic being evaluated (e.g., Figure \ref{fig:recchall}). Physical job characteristics such as, for example, the amount of ``time spent bending or twisting the body'' may be much more likely to be appraised as a challenging demand (but not a resource). Other \emph{types} of job requirements, however, such as a mental process like, ``scheduling work and activities'' might reasonably be expected to exhibit greater convergence. We suspect that there are other moderators that help explain this association/ disassociation between challenges and resources, and would like to incorporate variables such as a respondents' personality in future investigations.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.

@@

\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
Peterson, N. G., Mumford, M. D., Borman, W. C., Jeanneret, P. R., Fleishman, E. A., Levin, K. Y., Campion, M. A., Mayfield, M. S., Morgeson, F. P., Pearlman, K., et al. (2001). Understanding work using the occupational information network (o* NET): Implications for practice and research. \emph{Personnel Psychology}, \emph{54}(2), 451--492.
